---
title: "mating psychology"
author:
  - William Costello, Swansea University
  - Vania Rolón, Brunel University London
  - Andrew Thomas, Swansea University
  - David Schmitt, Brunel University London
output:
  html_document:
    toc: yes
---

```{r message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(psych)
library(lm.beta)

data <- read_csv("C:/Users/Vania/Desktop/psychology of incels/incel cleaned data.csv")
```

The hypotheses regarding mating-related variables were:

* Incel men will report more external and internal reasons for being single
* Incel men will report lower minimum mate preferences than non-incel men (15 traits plus overall, use Bonferroni-Holm correction)
* Incel men, more than non-incel men, will overestimate women’s minimum mate preferences and overemphasise the importance of physical-attractiveness

# Reasons for being single

```{r}
data_RBS <- data %>%
  filter(sex == 0 & incel == 0 | sex == 0 & incel == 1) %>%
  dplyr::select(., (c(incel, RBS_int, RBS_ext))) %>%
  group_by(incel) %>%
  mutate(RBS_intZ = scale(RBS_int), RBS_extZ = scale(RBS_ext)) %>%
  ungroup()

range(data_RBS$RBS_intZ, na.rm = TRUE)
sum(data_RBS$RBS_intZ > 3.30, na.rm = TRUE) #3 outliers
range(data_RBS$RBS_extZ, na.rm = TRUE)
sum(data_RBS$RBS_extZ > 3.30, na.rm = TRUE) #6 outliers

# Internal reasons
data_RBSint <- data_RBS %>%
  filter(RBS_intZ >= -3.30 & RBS_intZ <= 3.30)

favstats(~ RBS_int, incel, data = data_RBSint)

(leveneTest(RBS_int ~ as.factor(incel), data = data_RBSint))$`Pr(>F)` #homogeneity not met
t.test(RBS_int ~ incel, data = data_RBSint, var.equal = FALSE) #normal theory 95%CIs[.16, .54]

cohens_d(RBS_int ~ incel, data = data_RBSint)

set.seed(1993)
RBSint.boot <- Boot(lm(RBS_int ~ incel, data = data_RBSint), f = coef, R = 5000)
confint(RBSint.boot, level = .95, type = "norm")

# External reasons
data_RBSext <- data_RBS %>%
  filter(RBS_extZ >= -3.30 & RBS_extZ <= 3.30)

favstats(~ RBS_ext, incel, data = data_RBSext)

(leveneTest(RBS_ext ~ as.factor(incel), data = data_RBSext))$`Pr(>F)` #homogeneity not met
t.test(RBS_ext ~ incel, data = data_RBSext, var.equal = FALSE) #normal theory 95%CIs[.16, .54]

cohens_d(RBS_ext ~ incel, data = data_RBSext)

set.seed(1993)
RBSext.boot <- Boot(lm(RBS_ext ~ incel, data = data_RBSext), f = coef, R = 5000)
confint(RBSext.boot, level = .95, type = "norm")
```