---
title: "mental health analyses"
author:
  - William Costello, Swansea University
  - Vania Rolón, Brunel University London
  - Andrew Thomas, Swansea University
  - David Schmitt, Brunel University London
output:
  html_document:
    toc: yes
---

```{r message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(psych)
library(mosaic)
library(ggpubr)
library(car)
library(rstatix)
library(Hmisc)
library(MoEClust)
library(supernova)
library(lm.beta)
library(ppcor)
library(pwr)
library(apaTables)
library(probemod)
library(modplot)
library(interactions)
data <- read_csv("C:/Users/Vania/Desktop/psychology of incels/incel cleaned data.csv")
```

The hypotheses regarding mental health variables were:

* Incels will report lower-levels of wellbeing than non-incels, including higher-levels of depression, anxiety and loneliness, with lower-levels of life-satisfaction.

* Incels will score higher on sociosexual-desire and TIV, and increased sociosexualdesire and TIV will be more related to low-levels of wellbeing in incels than non-incels.

# Assessing reliability for sample subset

```{r}
alphaNFR <- (alpha(select(data %>% filter(sex == 0), c(NFR_1:NFR_6))))$total$raw_alpha
alphaME <- (alpha(select(data %>% filter(sex == 0), c(ME_1:ME_6))))$total$raw_alpha
alphaLoE <- (alpha(select(data %>% filter(sex == 0), c(LoE_1:LoE_6))))$total$raw_alpha
alphaRUM <- (alpha(select(data %>% filter(sex == 0), c(RUM_1:RUM_4))))$total$raw_alpha
alphaTIV <- (alpha(select(data %>% filter(sex == 0), c(NFR_1:RUM_4))))$total$raw_alpha
alphaMVS <- (alpha(select(data %>% filter(sex == 0), c(MVS_1:MVS_2_2))))$total$raw_alpha
alphaPQ9 <- (alpha(select(data %>% filter(sex == 0), c(NHSdepress_1:NHSdepress_8))))$total$raw_alpha
alphaGAD <- (alpha(select(data %>% filter(sex == 0), c(NHSdepress_9:NHSdepress_15))))$total$raw_alpha
alphalone <- (alpha(select(data %>% filter(sex == 0), c(lonely_1:lonely_3))))$total$raw_alpha
alphaSWL <- (alpha(select(data %>% filter(sex == 0), c(Q75_1:Q75_5))))$total$raw_alpha
alphasoides <- (alpha(select(data %>% filter(sex == 0), c(soides_1, soides_2, soides_3))))$total$raw_alpha
  
data.frame("Cronbach's alpha for TIV" = c(alphaNFR, alphaME, alphaLoE, alphaRUM, alphaTIV,
                                          alphaMVS, alphasoides, alphaPQ9, alphaGAD, alphalone, alphaSWL),
                                      row.names =  c("Need for recognition", "Moral elitism", "Lack of empathy", "Rumination", "TIV",
                                                     "Mate value", "SOI desire", "Depression", "Anxiety", "Loneliness", "Satisfaction with life"))
```

# Preparing for outliers and data filtering

A new sample subset was created by filtering the whole dataset by participants who were biologically male and answered the incel self-identification item. Age and ethnicity were selected for basic demographic information. Beyond the variables for the confirmatory hypotheses (i.e., mental health variables, MVS, TIV, and SOI desire), some exploratory variables were also selected. Z-scores by incel group (0 = non-incel, 1 = incel) were computed to remove outliers (Z-scores greater than +/- 3.30). Only age had any outliers (3 to be precise)

```{r}
data_mh <- data %>%
  dplyr::select(., (c(incel, sex, age, soides, MVS, 
                      PHQ9_mean, GAD_mean, lonely_mean, SWL_mean, PHQ9_all, GAD_all, lonely_all, SWL_all,
                      TIV_NFR, TIV_ME, TIV_LoE, TIV_RUM, TIV,
                      ethnic_1:ethnic_7, country, 
                      porn, forums, incel4life, blackpill, forumWellbeing, femopinion, feminist))) %>% #for exploratory purposes
  filter(sex == 0 & incel == 0 | sex == 0 & incel == 1)

data_mh <- data_mh %>%
  group_by(incel) %>%
  mutate(ageZ = scale(age),
         soidesZ = scale(soides),
         MVSZ = scale(MVS),
         PHQ9Z = scale(PHQ9_all), GADZ = scale(GAD_all), lonelyZ = scale(lonely_all), SWLZ = scale(SWL_all),
         PHQ9_meanZ = scale(PHQ9_mean), GAD_meanZ = scale(GAD_mean), lonely_meanZ = scale(lonely_mean), SWL_meanZ = scale(SWL_mean),
         NFRZ = scale(TIV_NFR), MEZ = scale(TIV_ME), LoEZ = scale(TIV_LoE), RUMZ = scale(TIV_RUM), TIVZ = scale(TIV))%>%
  ungroup()

#averaged variables
range(data_mh$ageZ, na.rm = TRUE) #3 outliers
range(data_mh$soidesZ, na.rm = TRUE)
range(data_mh$MVSZ, na.rm = TRUE)
range(data_mh$NFRZ, na.rm = TRUE)
range(data_mh$MEZ, na.rm = TRUE)
range(data_mh$LoEZ, na.rm = TRUE)
range(data_mh$RUMZ, na.rm = TRUE)
range(data_mh$TIVZ, na.rm = TRUE)
range(data_mh$PHQ9_meanZ, na.rm = TRUE)
range(data_mh$GAD_meanZ, na.rm = TRUE)
range(data_mh$lonely_meanZ, na.rm = TRUE)
range(data_mh$SWL_meanZ, na.rm = TRUE)
```

# Group comparisons

An initial look at mean age for incels vs non-incels showed a difference of approximately 5 years, thus an independent samples t-test was conducted to assess if this difference was significant so we would know to control for age (e.g., younger people may be more likely to score higher on TIV or mental health issues, thus if the incel sample is younger than the non-incel sample, controlling for age would be important)

## Age

```{r}
data_age <- data_mh %>%
  filter(ageZ >= -3.30 & ageZ <= 3.30)

hist(lm(age ~ as.factor(incel), data = data_age)$residuals)
qqPlot(lm(age ~ as.factor(incel), data = data_age)$residuals)

favstats(~ age, incel, data = data_age)

(leveneTest(age ~ as.factor(incel), data = data_age))$`Pr(>F)` #homogeneity not met
t.test(age ~ incel, data = data_age, var.equal = FALSE) 
cohens_d(age ~ incel, data = data_age)

set.seed(1993)
age.boot <- Boot(lm(age ~ incel, data = data_age), f = coef, R = 5000)
confint(age.boot, level = .95, type = "norm")
```

Incels were significantly younger (*M* = 27.94, *SD* = 7.26, *n* = 146) than non-incels (*M* = 32.98, *SD* = 9.66, *n* = 371), *t*(351.08) = -6.44, *p* < .001, *d* = .59, *95%BootCI*[-6.57, -3.50]. Thus, instead of computing independent samples t-tests to compare the two groups on our outcome variables (i.e., TIV, mental health, MVS, and SOI desire), we computed a series of multiple regressions using age as a control variable. These are currently on the main branch

### Tendencies for interpersonal victimhood

#### Need for recognition

```{r}
dataNFR <- data_mh %>%
  filter(NFRZ >= -3.30 & NFRZ <= 3.30 & ageZ >= -3.30 & ageZ <= 3.30) 
  
favstats(~ TIV_NFR, incel, data = dataNFR)

hist(lm(TIV_NFR ~ as.factor(incel), data = dataNFR)$residuals)
qqPlot(lm(TIV_NFR ~ as.factor(incel), data = dataNFR)$residuals) #looking alright

(leveneTest(TIV_NFR ~ as.factor(incel), data = dataNFR))$`Pr(>F)` #homogeneity met
NFRt <- t.test(TIV_NFR ~ incel, data = dataNFR, var.equal = TRUE) #normal theory 95%CIs[.16, .54]
NFRt
p.adjust(NFRt$p.value, method = "bonferroni" , 
         n = 5)
cohens_d(TIV_NFR ~ incel, data = dataNFR)

set.seed(1993)
NFR.boot <- Boot(lm(TIV_NFR ~ incel, data = dataNFR), f = coef, R = 5000)
confint(NFR.boot, level = .95, type = "norm")

#Exploring how age affects the model
summary(lm(TIV_NFR ~ incel, data = dataNFR))
lm.beta(lm(TIV_NFR ~ incel, data = dataNFR))
supernova(lm(TIV_NFR ~ incel, data = dataNFR))
summary(lm(TIV_NFR ~ age, data = dataNFR))
lm.beta(lm(TIV_NFR ~ age, data = dataNFR))
summary(lm(TIV_NFR ~ age + incel, data = dataNFR))
lm.beta(lm(TIV_NFR ~ age + incel, data = dataNFR))
supernova(lm(TIV_NFR ~ age + incel, data = dataNFR))
```

#### Moral elitism

```{r}
dataME <- data_mh %>%
  filter(MEZ >= -3.30 & MEZ <= 3.30)
  
favstats(~ TIV_ME, incel, data = dataME)

hist(lm(TIV_ME ~ as.factor(incel), data = dataME)$residuals)
qqPlot(lm(TIV_ME ~ as.factor(incel), data = dataME)$residuals) #looking good

(leveneTest(TIV_ME ~ as.factor(incel), data = dataME))$`Pr(>F)` #homogeneity NOT met
MEt <- t.test(TIV_ME ~ incel, data = dataME, var.equal = FALSE) #normal theory 95%CIs[.29, .61]
MEt
p.adjust(MEt$p.value, method = "bonferroni" , 
         n = 5)
cohens_d(TIV_ME ~ incel, data = dataME)

set.seed(1993)
ME.boot <- Boot(lm(TIV_ME ~ incel, data = dataME), f = coef, R = 5000)
confint(ME.boot, level = .95, type = "norm")
```

#### Lack of empathy

```{r}
dataLoE <- data_mh %>%
  filter(LoEZ >= -3.30 & LoEZ <= 3.30)
  
favstats(~ TIV_LoE, incel, data = dataLoE)
hist(lm(TIV_LoE ~ as.factor(incel), data = dataLoE)$residuals)
qqPlot(lm(TIV_LoE ~ as.factor(incel), data = dataLoE)$residuals) #looks alright

(leveneTest(TIV_LoE ~ as.factor(incel), data = dataLoE))$`Pr(>F)` #homogeneity NOT met
LoEt <- t.test(TIV_LoE ~ incel, data = data_mh, var.equal = FALSE) #normal theory 95%CIs[.10, .50]
LoEt
p.adjust(LoEt$p.value, method = "bonferroni" , 
         n = 5)
cohens_d(TIV_LoE ~ incel, data = dataLoE)

set.seed(1993)
LoE.boot <- Boot(lm(TIV_LoE ~ incel, data = dataLoE), f = coef, R = 5000)
confint(LoE.boot, level = .95, type = "norm")
```

#### Rumination

```{r}
dataRUM <- data_mh %>%
  filter(RUMZ >= -3.30 & RUMZ <= 3.30)
  
favstats(~ TIV_RUM, incel, data = dataRUM)

hist(lm(TIV_RUM ~ as.factor(incel), data = dataRUM)$residuals)
qqPlot(lm(TIV_RUM ~ as.factor(incel), data = dataRUM)$residuals) #not pretty

(leveneTest(TIV_RUM ~ as.factor(incel), data = dataRUM))$`Pr(>F)` #homogeneity met
RUMt <- t.test(TIV_RUM ~ incel, data = dataRUM, var.equal = TRUE) #normal theory 95%CIs[.47, .98]
RUMt
p.adjust(RUMt$p.value, method = "bonferroni" , 
         n = 5)
cohens_d(TIV_RUM ~ incel, data = dataRUM)

set.seed(1993)
RUM.boot <- Boot(lm(TIV_RUM ~ incel, data = dataRUM), f = coef, R = 5000)
confint(RUM.boot, level = .95, type = "norm")
```

#### Overall TIV

```{r}
dataTIV <- data_mh %>%
  filter(TIVZ >= -3.30 & TIVZ <= 3.30)
  
favstats(~ TIV, incel, data = dataTIV)

hist(lm(TIV ~ as.factor(incel), data = dataTIV)$residuals)
qqPlot(lm(TIV ~ as.factor(incel), data = dataTIV)$residuals) #good

(leveneTest(TIV ~ as.factor(incel), data = dataTIV))$`Pr(>F)` #homogeneity NOT met
TIVt <- t.test(TIV ~ incel, data = dataTIV, var.equal = FALSE) #normal theory 
TIVt
p.adjust(TIVt$p.value, method = "bonferroni" , 
         n = 5)
cohens_d(TIV ~ incel, data = dataTIV)

set.seed(1993)
TIV.boot <- Boot(lm(TIV ~ incel, data = dataTIV), f = coef, R = 5000)
confint(TIV.boot, level = .95, type = "norm")
```

### Mating measures

#### Sociosexual desires

```{r}
datasoides <- data_mh %>%
  filter(soidesZ >= -3.30 & soidesZ <= 3.30)
  
favstats(~ soides, incel, data = datasoides)

hist(lm(soides ~ as.factor(incel), data = datasoides)$residuals)
qqPlot(lm(soides ~ as.factor(incel), data = datasoides)$residuals)

leveneTest(soides ~ as.factor(incel), data = datasoides)$`Pr(>F)` #homogeneity NOT met
t.test(soides ~ incel, data = datasoides, var.equal = FALSE) #normal theory 95%CIs[.12, .92]
cohens_d(soides ~ incel, data = datasoides)

set.seed(1993)
soides.boot <- Boot(lm(soides ~ as.factor(incel), data = datasoides), f=coef, R = 5000)
confint(soides.boot, level = .95, type = "norm") 
summary(soides.boot)
```

#### Perceived mate value

```{r}
dataMVS <- data_mh %>%
  filter(MVSZ >= -3.30 & MVSZ <= 3.30)
  
favstats(~ MVS, incel, data = dataMVS)

hist(lm(MVS ~ as.factor(incel), data = dataMVS)$residuals)
qqPlot(lm(MVS ~ as.factor(incel), data = dataMVS)$residuals) #alright

leveneTest(MVS ~ as.factor(incel), data = dataMVS)$`Pr(>F)` #homogeneity NOT met
t.test(MVS ~ incel, data = dataMVS, var.equal = FALSE) #normal theory 95%CIs[-1.42, -.86]
cohens_d(MVS ~ incel, data = dataMVS)

set.seed(1993)
MVS.boot <- Boot(lm(MVS ~ as.factor(incel), data = dataMVS), f=coef, R = 5000)
confint(MVS.boot, level = .95, type = "norm") 
summary(MVS.boot)
```

### Wellbeing measures

#### Depression 

```{r}
datadepress <- data_mh %>%
  filter(PHQ9_meanZ >= -3.30 & PHQ9_meanZ <= 3.30)
  
favstats(~ PHQ9_mean, incel, data = datadepress)

hist(lm(PHQ9_mean ~ as.factor(incel), data = datadepress)$residuals)
qqPlot(lm(PHQ9_mean ~ as.factor(incel), data = datadepress)$residuals) #alright

leveneTest(PHQ9_mean ~ as.factor(incel), data = datadepress)$`Pr(>F)` #homogeneity met
PHQ9t <- t.test(PHQ9_mean ~ incel, data = datadepress, var.equal = TRUE) #normal theory 95%CIs[.42, .75]
PHQ9t
p.adjust(PHQ9t$p.value, method = "bonferroni" , 
         n = 4)
cohens_d(PHQ9_mean ~ incel, data = datadepress)

set.seed(1993)
PHQ9_mean.boot <- Boot(lm(PHQ9_mean ~ as.factor(incel), data = datadepress), f = coef, R = 5000)
confint(PHQ9_mean.boot, level = .95, type = "norm")
```

#### Anxiety

```{r}
dataGAD <- data_mh %>%
  filter(GAD_meanZ >= -3.30 & GAD_meanZ <= 3.30)
  
favstats(~ GAD_mean, incel, data = dataGAD)

hist(lm(GAD_mean ~ as.factor(incel), data = dataGAD)$residuals)
qqPlot(lm(GAD_mean ~ as.factor(incel), data = dataGAD)$residuals) #not the best, not the worst

leveneTest(GAD_mean ~ as.factor(incel), data = dataGAD)$`Pr(>F)` #homogeneity not met
GADt <- t.test(GAD_mean ~ incel, data = dataGAD, var.equal = FALSE) #normal theory 95%CIs[.32, .72]
GADt
p.adjust(GADt$p.value, method = "bonferroni" , 
         n = 4)
cohens_d(GAD_mean ~ incel, data = dataGAD)

set.seed(1993)
GAD_mean.boot <- Boot(lm(GAD_mean ~ as.factor(incel), data = dataGAD), f = coef, R = 5000)
confint(GAD_mean.boot, level = .95, type = "norm") 
```

#### Loneliness

```{r}
datalonely <- data_mh %>%
  filter(lonely_meanZ >= -3.30 & lonely_meanZ <= 3.30)
  
favstats(~ lonely_mean, incel, data = datalonely)

hist(lm(lonely_mean ~ as.factor(incel), data = datalonely)$residuals)
qqPlot(lm(lonely_mean ~ as.factor(incel), data = datalonely)$residuals) #BIG NOPE

leveneTest(lonely_mean ~ as.factor(incel), data = datalonely)$`Pr(>F)` #homogeneity not met
lonelyt <- t.test(lonely_mean ~ incel, data = datalonely, var.equal = FALSE) #normal theory 95%CIs[.40, .62]
lonelyt
p.adjust(lonelyt$p.value, method = "bonferroni" , 
         n = 4)
cohens_d(lonely_mean ~ incel, data = datalonely)

set.seed(1993)
lonely_mean.boot <- Boot(lm(lonely_mean ~ as.factor(incel), data = datalonely), f=coef, R = 5000)
confint(lonely_mean.boot, level = .95, type = "norm") 
```

#### Satisfaction with life

```{r}
dataSWL <- data_mh %>%
  filter(SWL_meanZ >= -3.30 & SWL_meanZ <= 3.30)
  
favstats(~ SWL_mean, incel, data = dataSWL)

hist(lm(SWL_mean ~ as.factor(incel), data = dataSWL)$residuals)
qqPlot(lm(SWL_mean ~ as.factor(incel), data = dataSWL)$residuals)

leveneTest(SWL_mean ~ as.factor(incel), data = dataSWL)$`Pr(>F)` #homogeneity met
SWLt <- t.test(SWL_mean ~ incel, data = dataSWL, var.equal = TRUE) #normal theory 95%CIs[-1.60, -.96]
SWLt
p.adjust(SWLt$p.value, method = "bonferroni" , 
         n = 4)
cohens_d(SWL_mean ~ incel, data = dataSWL)

set.seed(1993)
SWL_mean.boot <- Boot(lm(SWL_mean ~ as.factor(incel), data = dataSWL), f=coef, R = 5000)
confint(SWL_mean.boot, level = .95, type = "norm") 
```

# Chi-squares comparing proportion of incel vs non-incel men categorised as depressed and anxious

The PHQ9 divides people into 5 depression categories based on the following scores:

  - 0-4: not depressed
  - 5-9: mildly depressed
  - 10-14: moderately depressed
  - 15-19: moderately severely depressed
  - 20+ : severely depressed
  
Similarly the GAD7 has the following cutoffs for different anxiety categories:

  - 0-4: no anxiety
  - 5-9: mild anxiety
  - 10-14: moderate anxiety
  - 15+ : severe anxiety

As such, to run chi-square tests of independence, we created categorical versions for depression and anxiety using *PHQ9_all* and *GAD_all*

```{r}
data_mh <- data_mh %>%
  mutate(PHQ9_cat = ifelse(PHQ9_all < 5, 0,
                           ifelse(PHQ9_all < 10, 1,
                                  ifelse(PHQ9_all < 15, 2,
                                         ifelse(PHQ9_all < 20, 3, 4)))),
         GAD_cat = ifelse(GAD_all < 5, 0, 
                           ifelse(GAD_all < 10, 1, 
                                  ifelse(GAD_all < 15, 2, 3))))

#creating contingency table
tblPHQ9 <- xtabs(~ incel + PHQ9_cat, data = data_mh)
tblGAD <- xtabs( ~ incel + GAD_cat, data = data_mh)

rowPHQ9 <- prop.table(tblPHQ9, 1)
rowGAD <- prop.table(tblGAD, 1)

#running chi-squares
chisq.test(tblPHQ9) # X^2(4) = 40.21, p < .001 
chisq.test(tblGAD) # X^2(3) = 18.51, p < .001

#post hoc and corrections
padjPHQ9 <- .05/(nrow(tblPHQ9)*ncol(tblPHQ9)) #new alpha value is .005
critPHQ9 <- qnorm(padjPHQ9/2) #new critical value is |2.81|

padjGAD <- .05/(nrow(tblGAD)*ncol(tblGAD)) #new alpha value is .006
critGAD <- qnorm(padjGAD/2) #new critical value is |2.73|

#examine expected values and standardised residuals
PHQ9exp <- chisq.test(tblPHQ9)$expected
GADexp <- chisq.test(tblGAD)$expected
PHQ9res <- chisq.test(tblPHQ9)$stdres
GADres <- chisq.test(tblGAD)$stdres
```

The adjusted residual for severe depression is no longer significant when applying a Bonferroni correction, however, there is still a difference in the proportions for moderately severe and no depression

# Interaction between incel self-identification, and SOI desire, and TIV on mental health outcomes

## Correlations among SOI desire, TIV, and mental health outcomes

```{r}
rcorr(as.matrix(data_mh[,c("PHQ9_mean","GAD_mean", "lonely_mean", "SWL_mean", "soides", "TIV", "age")], type="pearson"))
dplyr::select(data_mh, c(PHQ9_mean, GAD_mean, lonely_mean, SWL_mean, soides, TIV, age)) %>%
  apa.cor.table(data_mh, show.conf.interval = TRUE, filename = "Table_4_incel_mental_health.doc", table.number = 3)
```

## Depression

```{r}
depress <- data_mh %>%
  filter(soidesZ >= -3.30 & soidesZ <= 3.30 &
           TIVZ >= -3.30 & TIVZ <= 3.30 &
           PHQ9_meanZ >= -3.30 & PHQ9_meanZ <= 3.30 &
           age > 18) #remove univariate outliers and NA values for age (6 total) to be able to get Mahalanobis distances

depressmahal <- lm(age ~ incel + soides + TIV + PHQ9_mean, data = depress)

depress$res <- depress$age - predict(depressmahal)
depress$mahal <- MoE_mahala(depressmahal, depress$res)

#critical value for chi-square num df = 4, at p = .001 is 18.477
sum(depress$mahal > 18.47) #17 multivariate outliers

depress.mod <- lm(PHQ9_mean ~ 1 + incel + soides + TIV + incel*soides + incel*TIV, data = depress)
summary(depress.mod)
supernova(depress.mod)$tbl$PRE[5] #gives change in R2 as a result of the incel-soides interaction
supernova(depress.mod)$tbl$PRE[6] #gives change in R2 as a result of the incel-TIV interaction
lm.beta(depress.mod)
```

## Anxiety

```{r}
anx <- data_mh %>%
  filter(soidesZ >= -3.30 & soidesZ <= 3.30 &
           TIVZ >= -3.30 & TIVZ <= 3.30 &
           GAD_meanZ >= -3.30 & GAD_meanZ <= 3.30 &
           age > 18) 

anxmahal <- lm(age ~ incel + soides + TIV + GAD_mean, data = anx)

anx$res <- anx$age - predict(anxmahal)
anx$mahal <- MoE_mahala(anxmahal, anx$res)

#critical value for chi-square num df = 4, at p = .001 is 18.47
sum(anx$mahal > 18.47) # 14 multivariate outliers

anx.mod <- lm(GAD_mean ~ 1 + incel + soides + TIV + incel*soides + incel*TIV, data = anx)
summary(anx.mod)
supernova(anx.mod)$tbl$PRE[5] #gives change in R2 as a result of the incel-soides interaction
supernova(anx.mod)$tbl$PRE[6] #gives change in R2 as a result of the incel-TIV interaction
lm.beta(anx.mod)
```

## Loneliness

```{r}
lone <- data_mh %>%
  filter(soidesZ >= -3.30 & soidesZ <= 3.30 &
           TIVZ >= -3.30 & TIVZ <= 3.30 &
           lonely_meanZ >= -3.30 & lonely_meanZ <= 3.30 &
           age > 18)

lonemahal <- lm(age ~ incel + soides + TIV + lonely_mean, data = lone)

lone$res <- lone$age - predict(lonemahal)
lone$mahal <- MoE_mahala(lonemahal, lone$res)

#critical value for chi-square num df = 4, at p = .001 is 18.47
sum(lone$mahal > 18.47) #15 multivariate outliers

lone.mod <- lm(lonely_mean ~ 1 + incel + soides + TIV + incel*soides + incel*TIV, data = lone)
summary(lone.mod)
supernova(lone.mod)$tbl$PRE[5] #gives change in R2 as a result of the incel-soides interaction
supernova(lone.mod)$tbl$PRE[6] #gives change in R2 as a result of the incel-TIV interaction
lm.beta(lone.mod)

set.seed(1993)
lone.mod.boot <- Boot(lone.mod, f=coef, R = 5000)
confint(lone.mod.boot, level = .95, type = "norm")

#Probing the incel*TIV interaction
#order matters in pickapoint (if interaction term is incel*TIV, then the function expects incel as the iv and TIV as the moderator, and returns an error if the lm does not have this order. Thus, I just moved the terms around from lone.mod and requested the effects of TIV on loneliness for non-incels and incels. Both are significant, however, the effect is stronger for non-incels.

pickapoint(lm(lonely_mean ~ 1 + soides + TIV + incel + soides*incel + TIV*incel, data = lone),
           dv ='lonely_mean', iv = 'TIV', mod = 'incel')

interact_plot(lm(lonely_mean ~ 1 + soides + TIV + incel + soides*incel + TIV*incel, data = lone),
              pred = TIV, modx = incel) + 
  theme_classic(base_size = 8) +
  ylab("Mean loneliness score") +
  xlab("Overall tendency for interpersonal victimhood")
```

## Satisfaction with life

```{r}
SWL <- data_mh %>%
  filter(soidesZ >= -3.30 & soidesZ <= 3.30 &
           TIVZ >= -3.30 & TIVZ <= 3.30 &
           SWL_meanZ >= -3.30 & SWL_meanZ <= 3.30 &
           age > 18)

SWLmahal <- lm(age ~ incel + soides + TIV + SWL_mean, data = SWL)

SWL$res <- SWL$age - predict(SWLmahal)
SWL$mahal <- MoE_mahala(SWLmahal, SWL$res)

#critical value for chi-square num df = 4, at p = .001 is 18.47
sum(SWL$mahal > 18.47) #17 multivariate outliers

SWL.mod <- lm(SWL_mean ~ 1 + incel + soides + TIV + incel*soides + incel*TIV, data = SWL)
summary(SWL.mod)
supernova(SWL.mod)$tbl$PRE[5] #gives change in R2 as a result of the incel-soides interaction
supernova(SWL.mod)$tbl$PRE[6] #gives change in R2 as a result of the incel-TIV interaction
lm.beta(SWL.mod)
```

# Exploratory analyses

## Other incel vs non-incel comparisons

Beyond our main hypotheses, we ran exploratory analyses comparing the proportion of incel and non-incel men in variables such as living with self-reported mental and physical conditions, education, employment status, living arrangements, political affiliation, relationship seeking, and consideration of getting plastic surgery

```{r}
data_exp <- data %>%
  dplyr::select(., (c(incel, sex, employ, edu, politic, `M Health`, `P Health`, living, relation, seekrelation, surgery))) %>%
  rename(mental = `M Health`, physical = `P Health`) %>%
  filter(sex == 0 & incel == 0 | sex == 0 & incel == 1)

data_exp <- data_exp %>%
  group_by(incel) %>%
  mutate(politicZ = scale(politic), surgeryZ = scale(surgery))%>%
  ungroup()

range(data_exp$politicZ, na.rm = TRUE) #no outliers for the politic variable
range(data_exp$surgeryZ, na.rm = TRUE) #none for surgery either
```

For education, original categories (see report) were collapsed into 0 = Secondary education or less, 1 = Undergraduate, 2 = Postraduate so we would have enough expected cases per cell to run a chi-square. Similarly, for employment stauts, original categories were collapsed into 0 = non-NEET and 1 = NEET. For living arrangements, old categories were collapsed into 0 = living alone, 1 = cohabiting (with a housemate or romantic partner), and 2 = living with carers (parents, family, or other)

### Mental and physical conditions

```{r}
#Self-reported mental conditions

tblmental <- xtabs(~ incel + mental, data = data_exp)
rowmental <- prop.table(tblmental, 1)
chisq.test(tblmental)
padjmental <- .05/(nrow(tblmental)*ncol(tblmental)) #.0083
critmental <- qnorm(padjmental/2) #|2.64|
mentalexp <- chisq.test(tblmental)$expected
mentalres <- chisq.test(tblmental)$stdres

#Self-reported physical conditions
data_exp <- data_exp %>%
  mutate(physical = ifelse(physical == 3, 0,
                           ifelse(physical == 2, 1,
                                  ifelse(physical == 1, 2, 99)))) #so physical is on the same scale as mental
tblphysical <- xtabs(~ incel + physical, data = data_exp)
rowphysical <- prop.table(tblphysical, 1)
chisq.test(tblphysical)
padjphysical <- .05/(nrow(tblphysical)*ncol(tblphysical)) #.0083
critphysical <- qnorm(padjphysical/2) #|2.64|
physicalexp <- chisq.test(tblphysical)$expected
physicalres <- chisq.test(tblphysical)$stdres
```

### Education

```{r}
data_exp <- data_exp %>%
  mutate(edu_cat = ifelse(edu < 3 | edu == 6, 0,
                          ifelse(edu == 3, 1, 
                                 ifelse(edu == 4 | edu == 5, 2, 99))))

tbledu <- xtabs(~ incel + edu_cat, data = data_exp)
rowedu <- prop.table(tbledu, 1)
chisq.test(tbledu) 

padjedu <-.05/(nrow(tbledu)*ncol(tbledu)) #new alpha value = .0083
critedu <- qnorm(padjedu/2) #new critical value of |2.64|

eduexp <- chisq.test(tbledu)$expected
edures <- chisq.test(tbledu)$stdres
```

### Employment

```{r}
data_exp <- data_exp %>%
  mutate(employ = ifelse(employ < 5 | employ == 6, 0, 1))

tblemploy <- xtabs(~ incel + employ, data = data_exp)
rowemploy <- prop.table(tblemploy, 1)
chisq.test(tblemploy)

padjemploy <-.05/(nrow(tblemploy)*ncol(tblemploy)) #new alpha value = .012
critemploy <- qnorm(padjemploy/2) #new critical value of |2.50|

employexp <- chisq.test(tblemploy)$expected
employres <- chisq.test(tblemploy)$stdres
```

### Living arrangements

```{r}
data_liv <- data_exp %>%
  mutate(living = ifelse(living == 1, 0,
                         ifelse(living == 2 | living == 3, 1,
                                ifelse(living == 4, 2, 99)))) %>%
  filter(living < 99)

tblliving <- xtabs(~ incel + living, data = data_liv)
rowliving <- prop.table(tblliving, 1)
chisq.test(tblliving)

padjliving <-.05/(nrow(tblliving)*ncol(tblliving)) #new alpha value = .008
critliving <- qnorm(padjliving/2) #new critical value of |2.64|

livingexp <- chisq.test(tblliving)$expected
livingres <- chisq.test(tblliving)$stdres
```

### Political orientation

```{r}
data_pol <- data_exp %>%
  filter(politic < 6) #removing apolitcal ppl

favstats(~ politic, incel, data = data_pol)

leveneTest(politic ~ as.factor(incel), data = data_pol)$`Pr(>F)` #homogeneity met
t.test(politic ~ incel, data = data_pol, var.equal = TRUE) #normal theory 95%CIs[-1.60, -.96]
cohens_d(politic ~ incel, data = data_pol)

set.seed(1993)
politic.boot <- Boot(lm(politic ~ as.factor(incel), data = data_pol), f=coef, R = 5000)
confint(politic.boot, level = .95, type = "norm") 

data_pol2 <- data_pol %>%
  filter(incel == 1) %>%
  mutate(politic_cat = ifelse(politic == 5, 1, 
                              ifelse(politic == 4, 1, 
                                     ifelse(politic == 3, 3, 
                                            ifelse(politic == 2, 0, 0)))))

data_pol2$politic_cat <- factor(data_pol2$politic_cat, levels = c('0', '1', '3'),
                              labels = c('Left-leaning','Right-leaning', 'Centre'))
                              
tblpolitic <- xtabs(~ incel + politic_cat, data = data_pol2)
rowpolitic <- prop.table(tblpolitic, 1)
```

### Relationship seeking

```{r}
data_love <- data_exp %>%
  filter(relation == 1 & seekrelation < 6) %>% #all the single gentlemen, all the single gentlmen, oh-oh-oh, oh-oh-oh-oh
  mutate(seekrelation = 6 - seekrelation) #recoding seekrelation so > scores equal > desire to seek relationship

favstats(~ seekrelation, incel, data = data_love)

leveneTest(seekrelation ~ as.factor(incel), data = data_love)$`Pr(>F)` #homogeneity met
t.test(seekrelation ~ incel, data = data_love, var.equal = TRUE) #normal theory 95%CIs[-1.60, -.96]
cohens_d(seekrelation ~ incel, data = data_love)

set.seed(1993)
seekrelation.boot <- Boot(lm(seekrelation ~ as.factor(incel), data = data_love), f=coef, R = 5000)
confint(seekrelation.boot, level = .95, type = "norm")

data_love <- data_love %>%
  mutate(love_cat = ifelse(seekrelation == 5, 1, 
                              ifelse(seekrelation == 4, 1, 
                                     ifelse(seekrelation == 3, 3, 
                                            ifelse(seekrelation == 2, 0, 0)))))
data_love$love_cat <- factor(data_love$love_cat, levels = c('0', '1', '3'),
                              labels = c('No','Yes', 'Not sure'))
                              
tbllove <- xtabs(~ incel + love_cat, data = data_love)
rowlove <- prop.table(tbllove, 1)
```

### Cosmetic surgery

```{r}
data_surgery <- data_exp %>%
  mutate(surgery = 6 - surgery) %>% #recode so greater scores = greater desire to get surgery
  filter(surgeryZ >= -3.30 & surgeryZ <= 3.30 ) #removes NAs even if there are no outliers

favstats(~ surgery, incel, data = data_surgery)

leveneTest(surgery ~ as.factor(incel), data = data_surgery)$`Pr(>F)` #homogeneity not met
t.test(surgery ~ incel, data = data_surgery, var.equal = FALSE)
cohens_d(surgery ~ incel, data = data_surgery)

set.seed(1993)
surgery.boot <- Boot(lm(surgery ~ as.factor(incel), data = na.omit(data_surgery)), f = coef, R = 5000)
confint(surgery.boot, level = .95, type = "norm")

data_surgery <- data_surgery %>%
  mutate(surgery_cat = ifelse(surgery == 5, 1, 
                              ifelse(surgery == 4, 1, 
                                     ifelse(surgery == 3, 3, 
                                            ifelse(surgery == 2, 0, 0)))))
data_surgery$surgery_cat <- factor(data_surgery$surgery_cat, levels = c('0', '1', '3'),
                              labels = c('No','Yes', 'Not sure'))
                              
tblsurgery <- xtabs(~ incel + surgery_cat, data = data_surgery)
rowsurgery <- prop.table(tblsurgery, 1)


```


## Basic data demographics

```{r}
data_mh <- data_mh %>%
  mutate(
    ethnicity = case_when(
      ethnic_1 == 1 & is.na(ethnic_2) & is.na(ethnic_3) & is.na(ethnic_4) & is.na(ethnic_5) & is.na(ethnic_6) & is.na(ethnic_7) &
        is.na(ethnic_8) ~ 1,
      ethnic_2 == 1 & is.na(ethnic_1) & is.na(ethnic_3) & is.na(ethnic_4) & is.na(ethnic_5) & is.na(ethnic_6) & is.na(ethnic_7) &
        is.na(ethnic_8) ~ 2,
       ethnic_3 == 1 & is.na(ethnic_1) & is.na(ethnic_2) & is.na(ethnic_4) & is.na(ethnic_5) & is.na(ethnic_6) & is.na(ethnic_7) &
        is.na(ethnic_8) ~ 3,
      ethnic_4 == 1 & is.na(ethnic_1) & is.na(ethnic_2) & is.na(ethnic_3) & is.na(ethnic_5) & is.na(ethnic_6) & is.na(ethnic_7) &
        is.na(ethnic_8) ~ 4,
      ethnic_5 == 1 & is.na(ethnic_1) & is.na(ethnic_2) & is.na(ethnic_3) & is.na(ethnic_4) & is.na(ethnic_6) & is.na(ethnic_7) &
        is.na(ethnic_8) ~ 5,
      ethnic_6 == 1 & is.na(ethnic_1) & is.na(ethnic_2) & is.na(ethnic_3) & is.na(ethnic_4) & is.na(ethnic_5) & is.na(ethnic_7) &
        is.na(ethnic_8) ~ 6,
      ethnic_7 == 1 & is.na(ethnic_1) & is.na(ethnic_2) & is.na(ethnic_3) & is.na(ethnic_4) & is.na(ethnic_5) & is.na(ethnic_6) &
        is.na(ethnic_8) ~ 7,
      ethnic_8 == 1 & is.na(ethnic_1) & is.na(ethnic_2) & is.na(ethnic_3) & is.na(ethnic_4) & is.na(ethnic_5) & is.na(ethnic_6) &
        is.na(ethnic_7) ~ 8,
      TRUE ~ 6))

data_mh$ethnic_cat <- factor(data_mh$ethnicity, levels = c('1', '2', '3', '4', '5', '6', '7', '8'),
                              labels = c('White','Black', 'South/Southeast Asian', 'Eastern Asian', 'Latino', 'Mixed', 'Other', 'Middle Eastern'))
data_mh$country_cat <- factor(data_mh$country, levels = c('0', '1', '2', '3'),
                          labels = c('US', 'UK', 'Other', 'Ireland'))

summary(data_mh$ethnic_cat)/nrow(data_mh)*100 #breakdown by ethnicity
summary(data_mh$country_cat)/nrow(data_mh)*100 #breakdown by country
```

## Which incels fair better?

  - Do watching porn, using forums, believing in the blackpill or that one will be an incel for life affect incel mental health?
  - Do incels who participate in forums perceive their wellbeing to have improved? (one-sample t w/forumWellbeing)
  - Do incels really believe in the blackpill? (one-sample t w/blackpill)
  
  - Have incels' opinions of women changed as a result of forum use? (one-sample t w/ femopinion) 
  - Are incels who participate in forums or watch more porn more feminist (or likely to identify as one)?
  
```{r}
data_incels <- data_mh %>%
  filter(incel == 1) %>%
  mutate(incel4life = 6 - incel4life, blackpill = 6 - blackpill, forumWellbeing = 6 - forumWellbeing, #recoding so > values = 
         femopinion = 6 - femopinion, feminist = 6 - feminist,                                        # > scores on these variables
         pornZ = scale(porn), incel4lifeZ = scale(incel4life), blackZ = scale(blackpill), forumWellbeingZ = scale(forumWellbeing), 
         femopinionZ = scale(femopinion), feministZ = scale(feminist))

#checking for outliers
range(data_incels$pornZ, na.rm = TRUE) #yup, one outlier when looking at the sum of cases that are > 3.30
range(data_incels$incel4lifeZ, na.rm = TRUE)
range(data_incels$blackZ, na.rm = TRUE)
range(data_incels$forumWellbeingZ, na.rm = TRUE)
range(data_incels$femopinionZ, na.rm = TRUE)
range(data_incels$feministZ, na.rm = TRUE)

incel_PHQ9.lm <- data_incels %>%
  filter(pornZ >= -3.30 & pornZ <= 3.30 ) %>%
  lm(PHQ9_mean ~ 1 + porn + forums + blackpill + incel4life, data = .)
summary(incel_PHQ9.lm)
lm.beta(incel_PHQ9.lm)

incel_GAD.lm <- data_incels %>%
  filter(pornZ >= -3.30 & pornZ <= 3.30 ) %>%
  lm(GAD_mean ~ 1 + porn + forums + blackpill + incel4life, data = .)
summary(incel_GAD.lm)
lm.beta(incel_GAD.lm)

incel_lonely.lm <- data_incels %>%
  filter(pornZ >= -3.30 & pornZ <= 3.30 ) %>%
  lm(lonely_mean ~ 1 + porn + forums + blackpill + incel4life, data = .)
summary(incel_lonely.lm)
lm.beta(incel_lonely.lm)

incel_SWL.lm <- data_incels %>%
  filter(pornZ >= -3.30 & pornZ <= 3.30 ) %>%
  lm(SWL_mean ~ 1 + porn + forums + blackpill + incel4life, data = .)
summary(incel_SWL.lm)
lm.beta(incel_SWL.lm)

t.test(data_incels$forumWellbeing, mu = 3)
t.test(data_incels$blackpill, mu = 3)
t.test(data_incels$incel4life, mu = 3) #only significant one
(favstats(~ incel4life, data = data_incels)$mean - 3)/favstats(~ incel4life, data = data_incels)$sd #effect size

#Finding percentages of incels who use forums who agree these have helped their wellbeing

data_forums <- data_incels %>%
  filter(forums == 1) %>%
  mutate(forum_cat = ifelse(forumWellbeing == 5, 1, 
                              ifelse(forumWellbeing == 4, 1, 
                                     ifelse(forumWellbeing == 3, 3, 
                                            ifelse(forumWellbeing == 2, 0, 0)))))

data_forums$forum_cat <- factor(data_forums$forum_cat, levels = c('0', '1', '3'),
                              labels = c('No','Yes', 'Not sure'))
                              
tblforum <- xtabs(~ incel + forum_cat, data = data_forums)
rowforum <- prop.table(tblforum, 1)

#Finding percentages of incels who believe, to some degree, in the blackpill vs not and in permanency of inceldom

data_incels <- data_incels %>%
  mutate(blackpill_cat = ifelse(blackpill == 5, 1, 
                              ifelse(blackpill == 4, 1, 
                                     ifelse(blackpill == 3, 3, 
                                            ifelse(blackpill == 2, 0, 0)))))

data_incels$blackpill_cat <- factor(data_incels$blackpill_cat, levels = c('0', '1', '3'),
                              labels = c('No','Yes', 'Not sure'))
                              
tblblackpill <- xtabs(~ incel + blackpill_cat, data = data_incels)
rowblackpill <- prop.table(tblblackpill, 1)


data_incels <- data_incels %>%
  mutate(incel4life_cat = ifelse(incel4life == 5, 1, 
                              ifelse(incel4life == 4, 1, 
                                     ifelse(incel4life == 3, 3, 
                                            ifelse(incel4life == 2, 0, 0)))))

data_incels$incel4life_cat <- factor(data_incels$incel4life_cat, levels = c('0', '1', '3'),
                              labels = c('No','Yes', 'Not sure'))
                              
tblincel4life <- xtabs(~ incel + incel4life_cat, data = data_incels)
rowincel4life <- prop.table(tblincel4life, 1)
```
